Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-06 prop_letter.tex
prop_letter.tex \section{Introduction} Update the comment...

The paper is organized as follows.   In Sec.\ \ref{sec:fuzzy} we begin by introducing the foundations of quantum probability space and fuzzy measurement.  We then move on to introduce the concept of quantum interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.  This QIVPM will provide the mathematical framework to quantify the impact of finite precision measurements on quantum mechanics.  For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.  This provides a way of resolving the Meyer-Mermin debate\nb\footnote{Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.  Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.

>>>>

The paper is organized as follows.   In Sec.\ \ref{sec:fuzzy} we begin by introducing the foundations of quantum probability space and fuzzy measurement.  We then move on to introduce the concept of quantum interval valued probability in Sec.\ \ref{sec:Interval-Uncertainty}.  This QIVPM will provide the mathematical framework to quantify the impact of finite precision measurements on quantum mechanics.  For instance, in Sec.\ \ref{sec:Kochen-Specker},  we quantify the domain of validity of a  contextual measurement, thus addressing the conditions under which the Kochen-Specker theorem applies.  This provides a way of resolving the Meyer-Mermin debate\nb\footnote{There is nothing found when google ``Meyer-Mermin debate.'' This
is not a very good name, since there are more people involve in this
debate. For example, Cabello~\citep{Cabello2002} and Larsson~\citep{Larsson2002}
attended the conference, and they commented on this issue as well.
They might not be very happy if we are our referees and only see Meyer
and Mermin's name??\\
Adán Cabello has referred to this as the second contextuality war~\citep{Cabello2017}.\\
Jochen Szangolies called this ``the Finite-Precision Problem''~\citep{Szangolies2015}.\\
D.M. Appleby doesn't refer this problem by any special name~\citep{Appleby_2005}...}, which is the main result of our Theorem \ref{cor:Kochen-Specker-IVPM}.  In Sec.\ \ref{sec:Gleason}, we study Gleason's theorem in the context of imprecise measurements, concluding that QIVPM provides a framework with quantitative bounds in which Gleason's theorem, while formally invalid in a universe with bounded resources, holds asymptotically in a mathematically precise way.  Finally, we present our conclusions in Sec.~\ref{sec:Conclusion}.
